A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-15 docs/vignette/191115_PMMB_DataWrangling_PM.Rmd
rerender

# Import and Format Data
## Non-wrangled trials

Data from the three follow trials were input manually from either PDF or word files.  
   - Gatton 2012  
   - Kingaroy 2012  
   - Emerald 2016

@@

## Functions
```{r functions}
fold_data <- function(new_DataFrame, template_DataFrame) {
   # This function formats a dataframe to have the same column order as a template data.frame
   # If columns are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
   # with NA values. 
   # Columns in the new_DataFrame, which are not in the template_DataFrame are appended to the right-hand-side
   # of the new_DataFrame
   # Using this function assists in joining the two data.frames together so columns are in the same order

@@

   new_DataFrame[,cnames2[!(cnames2 %in% cnames1)]] <-
      NA # adding column names to new_DataFrame which are in the template_DataFrame
   new_DataFrame <-
      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # arranges column names to new_DataFrame not in template_DataFrame

   return(new_DataFrame)
}
source(here("R/copy_class.R"))
source(here("R/replace_data.R"))
```

@@

#### AUDPC curve
```{r Herm_audpc, warning=FALSE}

@@

#### AUDPC curve
```{r King11_AUDPC, warning=FALSE}
library(ggplot2)

@@

### Kingaroy 2016  
Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
```{r King16_dataimport}
# Yield data from 2016 Hermitage trial with final disease severity
King_16 <-
   read.xlsx(
      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
      sheet = "Kingaroy",
      startRow = 1,
      colNames = TRUE
   )[1:28, 1:9]

@@

@@

# I have comment out this code because it does not replace the control plots properly as there is nothing to separate them from each other
# insert new calculations into data
#PM_MB_means <-   
   # replace_data(template_data = PM_MB_means,
   #                          new_data = Fogerty_17_m,
   #                          new_data_column = "AUDPC_m",
   #                          ignore_columns = c(5:8,10:16,29:46),
   #                          subset_factor = "mung1617/02")

@@

#### Define treatment data
```{r Well_18_treatmentDefine}
Well_18_dat <- Well_18 %>%
   mutate(trade_name = 
             case_when(Fung.Trt == 1 ~ "Folicur",
                       Fung.Trt == 3 ~ "Throttle",
                       Fung.Trt == 2 ~ "Custodia",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             case_when(Fung.Trt == 1 ~ "tebuconazole",
                       Fung.Trt == 3 ~ "propiconazole",
                       Fung.Trt == 2 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(dose_ai.ha = 
             case_when(Fung.Trt == 1 ~ 60,
                       Fung.Trt == 2 ~ 62,
                       Fung.Trt == 3 ~ 125,
                       Fung.Trt == 4 ~ 0,
                       TRUE ~ 9999))%>%
   mutate(Row.Spacing = 
             case_when(Row.Sp.Trt == 1 ~ 0.25,
                       Row.Sp.Trt == 2 ~ 0.5,
                       Row.Sp.Trt == 3 ~ 1,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_2 = 
             case_when(Fung.Trt <= 3 ~ as.Date("2018-04-16", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_1 = 
             case_when(Fung.Trt == 4 ~ as.Date(NA),
                       Fung.Trt == 1 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 2 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 3 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Fung.Trt <= 3 ~ 2,
                       Fung.Trt == 4 ~ 0,
                       TRUE ~ NA_real_))

@@

# For some weird reason standard deviations are coming back NA in the code above
Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Well_18_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

# insert new calculations into data
PM_MB_means <- 
   replace_data(template_data = PM_MB_means, 
                            new_data = Well_18_m, 
                            new_data_column = c("total_fungicide","AUDPC_m", "AUDPC_sd"),
                            filter_cols = c("trial_ref","year","location","n_treatment"))

@@

```{r Save_PM_MB_means, echo=TRUE}

>>>>

# Data wrangling
This file is not complete and there are a number of things that need checking
   - Mean squares are only calculated for the triazoles and controls
   - If the years for each trial are input correctly
   - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
   - AUDPC needs to be checked for starting dates and if trials have been omitted
   - Check that what is generated from this file matches the main file and update
   - write.csv should have row.names = FALSE

@@

## Functions
```{r functions}
fold_data <- function(new_DataFrame, template_DataFrame) {
   # This function formats a dataframe to have the same column order as a template data.frame
   # If colums are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
   # with NA values. 
   # Columns in the new_DataFrame, which are not in the template_DataFrame are appended to the right-hand-side
   # of the new_DataFrame
   # Using this function assists in joining the two data.frames together so colums are in the same order

@@

   new_DataFrame[,cnames2[!(cnames2 %in% cnames1)]] <-
      NA # adding column names to new_DataFrame which are in the template_DataFrame
   new_DataFrame <-
      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # aranges column names to new_DataFrame not in template_DataFrame

   return(new_DataFrame)
}
source(here("R/copy_class.R"))
source(here("R/data_mesh.R"))
```

@@

#### AUDPC curve
```{r Herm_audpc}

@@

#### AUDPC curve
```{r King11_AUDPC}
library(ggplot2)

@@

### Kingaroy 2016  
Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
```{r Herm16_dataimport}
# Yield data from 2016 Hermitage trial with final disease severity
King_16 <-
   read.xlsx(
      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
      sheet = "Kingaroy",
      startRow = 1,
      colNames = TRUE
   )[1:28, 1:9]

@@

#dim(Fogerty_17)   # 162 rows , 43 Columns

@@

# I have comment out this code because it does not replace the control plots properly
# insert new calculations into data
# PM_MB_means <-   replace_data(template_data = PM_MB_means, 
#                             new_data = Fogerty_17_m, 
#                             new_data_column = "AUDPC_m", 
#                             ignore_columns = c(5:8,10:16,29:46))
#

@@

#### Define treatment data
```{r Well_18_treatmentDefine}
Well_18_dat <- Well_18 %>%
   mutate(trade_name = 
             case_when(Fung.Trt == 1 ~ "Folicur",
                       Fung.Trt == 3 ~ "Throttle",
                       Fung.Trt == 2 ~ "Custodia",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             case_when(Fung.Trt == 1 ~ "tebuconazole",
                       Fung.Trt == 3 ~ "propiconazole",
                       Fung.Trt == 2 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(dose_ai.ha = 
             case_when(Fung.Trt == 1 ~ 60,
                       Fung.Trt == 2 ~ 62,
                       Fung.Trt == 3 ~ 125,
                       Fung.Trt == 4 ~ 0,
                       TRUE ~ 9999))%>%
   mutate(Row.Spacing = 
             case_when(Row.Sp.Trt == 1 ~ 0.25,
                       Row.Sp.Trt == 2 ~ 0.5,
                       Row.Sp.Trt == 3 ~ 1,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_2 = 
             case_when(Fung.Trt <= 3 ~ as.Date("2018-04-16", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_1 = 
             case_when(Fung.Trt == 4 ~ as.Date(NA),
                       Fung.Trt == 1 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 2 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 3 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Fung.Trt <= 3 ~ 2,
                       TRUE ~ NA_real_))

@@

# For some weird reason standard deviations are comming back NA in the code above
Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Well_18_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

# insert new calculations into data
PM_MB_means <- 
   replace_data(template_data = PM_MB_means, 
                            new_data = Well_18_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd"),
                            filter_cols = c("trial_ref","year","location","n_treatment"))

# check the same dimensions
dim(Well_18_m) ==
dim(PM_MB_means[PM_MB_means$trial_ref == "mung1718/01",])

   # Not sure why replace_data will not replcae the following columns
   PM_MB_means[c(324: 347),
               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] #<-
      Well_18_m[,c("AUDPS_m", "AUDPS_sd","Inc_Ms")]

@@

```{r Save_PM_MB_means, eval=FALSE, include=FALSE}
